Gradual Soundness: Lessons from Static Python

### 2022-01-13 pj-7.1/paper.tex
pj: sec 4, reword para on not-modeled features

The model intentionally does not cover all of Python.
Some aspects of \SP{} are left out because they are straightforward to
handle soundly.
These include primitive types~\cref{s:c-types} and strict modules~\cref{s:strict-mod}.
Aspects of \SP{} that do not pertain to soundness, such as the quality of error messages,
are also omitted.
Other Python features are left out because their \SP{} semantics is identical
to the baseline Python semantics.
These features include \code{eval}, first-class classes, multiple inheritance, and module-level cells;
see \cref{s:impl} for further discussion.
Lastly, the model does not include type-directed optimizations.
Validating the correctness of optimizations is a separate task that requires
significant components: a model of the \SP{} bytecode and a faithful
rendering of its type-based transformations.
Our model establishes soundness as a baseline.
Future work can use soundness as a starting point for compiler verification,
or informally leverage soundness to reason about possible optimizations.

>>>>

The model intentionally does not cover all of Python.
Some aspects of \SP{} are left out because they are straightforward to
handle soundly.
These include primitive types~\cref{s:c-types} and strict modules~\cref{s:strict-mod}.
Aspects of \SP{} that do not pertain to soundness, such as the quality of error messages,
are also omitted.
Other Python features are left out either because their \SP{} semantics is identical
to the baseline Python semantics or because they would entail a separate project~(\cref{s:impl}).
In particular, modelling type-directed optimization would require substantial
components: a model of the \SP{} bytecode and a faithful rendering of its
transformations.
Our model establishes soundness as a baseline.
Future work can use soundness as a starting point for compiler verification,
or informally leverage soundness to reason about possible optimizations.
